---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# General information

The WID-BC-index is computed using methylation data to highlight the potential epigenetic risk score. 

The package is aimed to enable research use of the WID-BC-index by facilitating computation from methylation data.

The input is a beta methylation matrix, for instance derived after quality control and normalisation of data obtained from the Illumina MethylationEPIC (preferred) or Illumina Methylation450k Array (caveat: not all WID-BC-index CpGs are represented on the 450k array). 

The use is as follows:

`WID_BC(beta)`

# Examples

Example dataset

```{r fig.align  = "center", fig.width = 2.5, fig.height = 3.5}

library(WID.BC)
data %>%
  ggplot(aes(x = type,
             y = WID_BC)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  xlab("") +
  ylab("WID-BC-index")
```

# Reference

[1] Barrett, J., Herzog., C., et al. (2021). "The WID-BC-index identifies women with primary poor prognostic breast cancer based on DNA methylation in cervical samples" (under review)
